\LARGE \bf Object Detection-Based Behaviour using Deep-Learning on Thymio

### 2018-06-01 paper/paper.tex
paper finished
minor changes to paper
paper done

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The ability to classify objects in both space and domain is encoded in an enormous variety of species on the planet. Recently, deep learning approaches have been developed to make machines able to mimic the same task with interesting results. With this paper, we propose a minimal architecture to archive the same goal using a cheap two-wheels robot, the Thymio, with a mounted frontal camera in order to make it moves based on the objects detected in the surrounding. 
\end{abstract}

@@

Specifically, our robot will wait for a user-specified class, e.g. \emph{dog}, and, when it finds it using the object detecttion model on the camera image, it moves towards the object by keeping it in the middle of its view. We also implemented a PID-based algorithm to avoid obstacles and properly stop in front of the founded item.

@@

\section{Architecture overview}
We used the Robotic Operating System,\cite{ROS}, since it is \emph{de facto} the state of the art. Our architecture is composed by:
\begin{enumerate}
	\item A robot with a mounted camera and with a ROS node running on the on-board computer;
	\item A web server running the Object Detection model;
	\item A ROS node running on a local machine that controls the robot.
\end{enumerate}
As a robot, we used the \emph{MightyThymio} \cite{guzzi2018eaai}, which is a robot developed on top of the Thymio, a small mass-produced mobile robot usually used in primary and secondary education. The MightyThymio has a powerful Odroid C1 on board, a 1GB quad-core ARM Linux machine, with a HD camera mounted on top. The authors also implemented a ROS node to communicate with it and open-sourced the code.

@@

\subsection*{Local ROS node}
We created a new ROS node to communicate with the running node on the MightyThymio, in order to control it accordingly with a specified behaviour based on the object detected by the model. The user specifies a set of target classes, for example \emph{dog} and \emph{cat}. Then our node, after having subscribed to the camera topic of the MightyThymio, sends the fetched image to the model hosted on a Web  Server through an HTTP request and gets as response the detected classes and their bounding boxes. In case there is no target object, the robot enters in \texttt{exploration} mode and starts spinning around. When one or more of the target classes are found simultaneously, the robot will go towards the target with the biggest bounding box area while keeping it in the center of the camera in order to follow it. In addition, we have an obstacle-avoiding algorithm in order to properly stop the Thymio before it hits the target.

@@

To accomplish this task, we defined two PIDs, one for the linear velocity and one for the angular velocity. The errors are $e_l$ for the linear PID and $e_a$ for the angular PID, defined as follows. We denote the front sensor set as $S_f$ and the rear sensor set as $S_r$, where each element in the set is a double representing the value from the sensor. In our case the cardinality of the sets are $|S_f| = 5$ and $|S_r|=2$.
\begin{align}
	e_l &= \sum\limits_{i=0}^{|S_f|} S_f(i) - \sum\limits_{i = 0}^{|R_f|} R_f(i) \\
	e_a &= (\sum\limits_{i=0}^{\frac{|S_f|}{2}} S_f(i) - \sum\limits_{i = \frac{|S_f|}{2} }^{|S_f|} S_f(i))  \\
	&- (\sum\limits_{i=0}^{\frac{|R_f|}{2}} R_f(i) - \sum\limits_{i = \frac{|R_f|}{2} }^{|R_f|} R_f(i))  \notag
\end{align}
The linear error, $e_l$, is just the sum of all the frontal sensors values minus the rear sensors values.  The angular error is defined as the difference between each pair of sensors on the left and on the right. In both the equations, we subtract the frontal values from the rear ones in order to invert the sign of the PID output so that when there is an obstacle in front of the robot, the velocity is negative and vice-versa.

@@

\includegraphics[width=0.25\linewidth]{images/leds/1}	
\includegraphics[width=0.25\linewidth]{images/leds/2}	
\includegraphics[width=0.25\linewidth]{images/leds/3}	
\end{center}
\begin{center}
\includegraphics[width=0.25\linewidth]{images/leds/4}	
\includegraphics[width=0.25\linewidth]{images/leds/5}
\end{center}
\caption{On board LEDs}
\end{figure}
A video showing the point of view of the Thymio while moving towards a \emph{cup} can be found \href{https://drive.google.com/open?id=1tZJpsfvfZGCGxunPWGHa3pLJnMj5mfOd}{here}\footnote{\texttt{https://drive.google.com/open?id=1tZJpsfvfZGCGxunPWGHa3pLJnMj5mfOd}}, and the third person view \href{https://drive.google.com/open?id=1Y5PMDQD8Aw0vxOK5yE5YwfiWLsMvXp-t}{here}\footnote{\texttt{https://drive.google.com/open?id=1Y5PMDQD8Aw0vxOK5yE5YwfiWLsMvXp-t}}.
\section{Conclusion}
In this paper, we presented a light and scalable architecture that uses a real-time Object Detection model to correctly find objects in the surrounding environment and to perform actions based on them. Moreover, because the only  hardware constraint is the camera, our work can be used into similar robots running ROS  to extend their functionalities. Furthermore, since we used YOLO to perform the classification task, the model can be easily re-trained with other classes to increase the context domain. This symbiosis between Deep Learning and Robotics highlights the power of both areas by creating new interesting use cases and scenarios in which both disciplines can shine.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The ability to classify objects in both space and domain is encoded in an enormous variety of species on the planet. Recently, deep learning approaches have been developed to make machines able to mimic the same task with interesting results. With this paper, we propose a minimal architecture to achieve the same goal using a cheap two-wheels robot, the Thymio, with a mounted frontal camera in order to make it moves based on the objects detected in the surrounding. 
\end{abstract}

@@

Specifically, our robot will wait for a user-specified class, e.g. \emph{dog}, and, when it finds it using the object detecttion model on the camera image, it moves towards the object by keeping it in the middle of its view. We also implemented a PID-based algorithm to avoid obstacles and properly stop in front of the found item.

@@

\section{Architecture overview}
We used the Robotic Operating System,\cite{ROS}, since it is \emph{de facto} the state of the art for robotics. The architecture is composed by:
\begin{enumerate}
	\item A robot with a mounted camera and with a ROS node running on the on-board computer;
	\item A web server running the Object Detection model;
	\item A ROS node running on a local machine that controls the robot.
\end{enumerate}
As a robot, we used the \emph{MightyThymio} \cite{guzzi2018eaai}, which is a robot developed on top of the Thymio, a small mass-produced mobile robot usually used in primary and secondary education. The MightyThymio has a powerful Odroid C1 on board, a 1GB quad-core ARM Linux machine, with a HD camera mounted on top. The authors also implemented a ROS node to communicate with it and open-sourced the code.

@@

\subsection*{Local ROS node}
We created a new ROS node to communicate with the running node on the MightyThymio, in order to control it accordingly with a specific behaviour based on the object detected by the model. The user specifies a set of target classes, for example \emph{dog} and \emph{cat}. Then our node, after having subscribed to the camera topic of the MightyThymio, sends the fetched image to the model hosted on a Web  Server through an HTTP request and gets as response the detected classes and their bounding boxes. In case there is no target object, the robot enters in \texttt{exploration} mode and starts spinning around. When one or more of the target classes are found simultaneously, the robot will go towards the target with the biggest bounding box area while keeping it in the center of the camera in order to follow it. In addition, we have an obstacle-avoiding algorithm in order to properly stop the Thymio before it hits the target.

@@

To accomplish this task, we defined two PIDs, one for the linear velocity and one for the angular velocity. The errors are $e_l$ for the linear PID and $e_a$ for the angular PID, defined as follows. We denote the front sensor set as $S_f$ and the rear sensor set as $S_r$, where each element in the set is a double representing the value from the sensor. In our case the cardinality of the sets are $|S_f| = 5$ and $|S_r|=2$.
\begin{align}
	e_l &= \sum\limits_{i=0}^{|S_f|} S_f(i) - \sum\limits_{i = 0}^{|R_f|} R_f(i) \\
	e_a &= \sum\limits_{i=0,k=|S_f|}^{\frac{|S_f|}{2}} S_f(i) - S_f(k) - \sum\limits_{i=0,k=|R_f|}^{\frac{|R_f|}{2}} R_f(i) - R_f(k)
  \notag
\end{align}
The linear error, $e_l$, is just the sum of all the frontal sensors values minus the rear sensors values.  The angular error is defined as the difference between each pair of sensors on the left and on the right. In both the equations, we subtract the frontal values from the rear ones in order to invert the sign of the PID output so that when there is an obstacle in front of the robot, the velocity is negative and vice-versa.

@@

\includegraphics[width=0.25\linewidth]{images/leds/1}	
\includegraphics[width=0.25\linewidth]{images/leds/2}	
\includegraphics[width=0.25\linewidth]{images/leds/3}	
\end{center}
\begin{center}
\includegraphics[width=0.25\linewidth]{images/leds/4}	
\includegraphics[width=0.25\linewidth]{images/leds/5}
\end{center}
\caption{On board LEDs}
\end{figure}
A video showing the point of view of the Thymio while moving towards a \emph{cup} can be found \href{https://drive.google.com/open?id=1tZJpsfvfZGCGxunPWGHa3pLJnMj5mfOd}{here}\footnote{\texttt{https://drive.google.com/open?id=1tZJpsfvfZGCGxunPWGHa3pLJnMj5mfOd}}, and the third person view \href{https://drive.google.com/open?id=1Y5PMDQD8Aw0vxOK5yE5YwfiWLsMvXp-t}{here}\footnote{\texttt{https://drive.google.com/open?id=1Y5PMDQD8Aw0vxOK5yE5YwfiWLsMvXp-t}}. We open-source all the project, the code can be found in our \href{https://github.com/FrancescoSaverioZuppichini/Robotics-Final-Project}{GitHub repository }\footnote{\texttt{https://github.com/FrancescoSaverioZuppichini/Robotics-Final-Project}}.

\section{Conclusion}
In this paper, we presented a light and scalable architecture that uses a real-time Object Detection model to correctly find objects in the surrounding environment and to perform actions based on them. Moreover, because the only  hardware constraint is the camera, our work can be used into similar robots running ROS  to extend their functionalities. Furthermore, since we used YOLO to perform the classification task, the model can be easily re-trained with other classes to increase the context domain. This symbiosis between Deep Learning and Robotics highlights the power of both areas by creating new interesting use cases and scenarios in which both disciplines can shine.
